Tennis doubles and ghosts

### 2022-06-23 inst/tennis.Rmd
consistentification

---
title: "Tennis doubles and ghosts"
output: bookdown::html_document2
---

@@

```{r}
H <- hyper2()

@@

```{r}
tennis <- H

@@

```{r}
tennis_ghost <- H

@@

```{r}
(tennis_maxp <- maxp(tennis))
(tennis_ghost_maxp <- maxp(tennis_ghost))
```

@@

```{r}
equalp.test(tennis)
```

@@

```{r}
specificp.test(tennis_ghost,"G",0.0001)  # nonzero value needed to avoid triggering known R bug
```

@@

```{r}
(M <- hessian(tennis,indep(tennis_maxp),border=TRUE))
```

@@

```{r}
eigen(M,TRUE,TRUE)$values # one value is zero to numerical precision; the rest should be <0
```

@@

```{r,label=savecurlingdataset}
save(tennis,tennis_maxp,tennis_ghost, tennis_ghost_maxp,file="tennis.rda")
```

>>>>

s---
title: "Tennis doubles and ghosts"
output: bookdown::html_document2
---

@@

```{r defineHhyper2}
H <- hyper2()

@@

```{r addtohyper2H}
tennis <- H

@@

```{r doghoststuff}
tennis_ghost <- H

@@

```{r maximizeghostlike,cache=TRUE}
(tennis_maxp <- maxp(tennis))
(tennis_ghost_maxp <- maxp(tennis_ghost))
```

@@

```{r doequalptest,cache=TRUE}
equalp.test(tennis)
```

@@

```{r specificptesthere,cache=TRUE}
specificp.test(tennis_ghost,"G",0.0001)  # nonzero value needed to avoid triggering known R bug
```

@@

```{r hessianmatrix}
(M <- hessian(tennis,indep(tennis_maxp),border=TRUE))
```

@@

```{r eigenwork}
eigen(M,TRUE,TRUE)$values # one value is zero to numerical precision; the rest should be <0
```

@@

```{r,label=saveghosttennisdataset}
save(tennis,tennis_maxp,tennis_ghost, tennis_ghost_maxp,file="tennis.rda")
```
